A Gravitationally Lensed Supernova with an Observable Two-Decade Time Delay

### 2020-06-23 Paper/Science/main.tex

One promising method uses %time delays of 
gravitational lens systems in which a background
source appears as multiple images that arrive to the observer with relative delays \cite{einstein_lens_1936}.
%, which %for a given lens potential 
When such a strongly-lensed source is variable, one can measure the time delay between any pair of lensed images and derive a ratio of angular diameter distances to the foreground lens and background source. 
This distance ratio is sensitive to cosmological parameters, such as 
%the expansion rate of the universe, 
$H_0$  and the dark energy equation of state, $w$ \cite{refsdal_possibility_1964,coe_cosmological_2009,linder_lensing_2011}.
In recent years this method has been very successfully applied to lensed
quasars \cite{suyu_cosmology_2014,bonvin_cosmograil_2019}, with six high-precision measurements to date \cite{wong_h0licow_2019}. As this sample of time delay lenses grows to several dozen, it is expected to deliver a measurement of $H_0$ with 1\% precision \cite{suyu_cosological_2018}.

Gravitationally lensed SN with multiple images present an attractive new addition to this field. Most notably, SN exhibit relatively simple photometric behavior, with well-understood light curve shapes and colors---a contrast to the stochastic variation of quasars.  However, the exploration of lensed SN time delay cosmography has been hindered by their rarity.  To date, there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}. The first, {\it SN Refsdal}, was a peculiar Type II SN whose image with the longest delay was missed \cite{kelly_SNRefsdal_2016}. The second, {\it SN 2016geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2020}. Here we present the discovery 
of a third lensed SN resolved into multiple images: \SNABC.

@@

%BibTeX users: After compilation, comment out the following two lines and paste in
% the generated .bbl file. 
\clearpage
\begin{figure*}
    \centering
    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
    \caption{Overview of the MACSJ0138 cluster field and the locations of the \SNABC images  (SN1--3) and its multiply-imaged host galaxy (H1--4). The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.  Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.  The three-color images are generated from the WFC3/IR filters as indicated; panels $bcd$ show the imaging from July 2016 where the SN was visible and $efg$ show the later imaging from July 2019 where the the SN has faded away.  All panels use the late-epoch F125W imaging for the green channel.  Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use to constrain the transient classification as a likely Ia supernova explosion and to constrain the relative age of each SN image.}

    \label{fig:layout}
\end{figure*}
\clearpage
\begin{figure}[h]
    \centering
    \includegraphics[draft=False, width=\textwidth]{Paper/Figures/classification_contours_timeline.pdf}
    \caption{Classification information for SN Requiem based on its position in color-magnitude space. (left) Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green).  These population contours are drawn to enclose 68\% (interior solid lines) and 95\% (exterior shaded regions) of each SN population.  Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time. Open markers show the observed photometry of the SN. Dotted vertical lines mark the magnification correction based on the lens modeling, terminating in closed markers with error bars that show the magnitude uncertainty, which is dominated by the lens modeling uncertainty.  (right) The evolution of a typical Type Ia SN at $z=1.95$ in observed color-mag space is shown by a colored line, with the color indicating SN age in observer-frame days relative to peak brightness.  White diamonds correspond to the times labeled on the colorbar at right. Grey shading shows the typical range of luminosities observed for the Type Ia SN population in the nearby universe \cite{wang_determination_2006}. An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6/#/}{https://plot.ly/~jpierel/6/#/}
    \label{fig:class}
    }
\end{figure}

@@

\midrule
\textit{1}  & $112^{+20}_{-38}$ & -- & $3.9\pm0.5$ & --\\
\textit{2} & $-27^{+26}_{-6}$ & $139^{+63}_{-23}$ & $7\pm3$ & $101\pm62$ \\
\textit{3} & $88^{+15}_{-15}$ & $16^{+19}_{-19}$ & $5\pm1$ & $19\pm34$ \\
\textit{4} & -- & -- & $0.4\pm0.2$ & $7761\pm541$\\

@@

The Cosmic Dawn Center of Excellence funded by the Danish National Research Foundation under grant No. 140.

@@

\begin{table}[h]
\centering
\begin{tabular}{ccccccr}
    \multicolumn{1}{c}{Telescope} & \multicolumn{1}{c}{Instrument} & \multicolumn{1}{c}{$\lambda_\mathrm{obs}$} & \multicolumn{1}{c}{Observation Date} & \multicolumn{1}{c}{MJD} & \multicolumn{1}{c}{SN} & \multicolumn{1}{c}{Exp. Time (s)}\\

\midrule
\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.1556 &   & 212 \\ % AOR r58785536
\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.1556 &   & 241 \\
\textit{HST}     & ACS/WFC   & F555W                     & 2016-06-03 21:50:43 & 57542.9102 &   & 5214 \\
\textit{HST}     & WFC3/IR   & F160W                     & 2016-07-18 23:14:50 & 57587.9686 & + & 1611 \\
\textit{HST}     & WFC3/IR   & F105W                     & 2016-07-19 00:43:47 & 57588.0304 & + & 3611 \\ 
\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.6078 &   & 468 \\ % AOR r58289152
\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.6078 &   & 581 \\
\midrule
\textit{HST}     & WFC3/IR   & F110w                     & 2019-07-13 20:53:16 & 58677.8703 &   & 706 \\ 
\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-14 22:16:01 & 58678.9278 &   & 353 \\ 
\textit{HST}     & WFC3/IR   & F125W                     & 2019-07-19 21:27:30 & 58683.8941 &   & 706 \\ 
\textit{HST}     & WFC3/UVIS & F814W                     & 2019-07-21 18:50:53 & 58685.7853 &   & 912 \\ 
\textit{HST}     & WFC3/UVIS & F390W                     & 2019-07-21 19:01:06 & 58685.7924 &   & 1272 \\ 
\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-21 22:42:22 & 58685.9461 &   & 353 \\ 
\textit{VLT}     & MUSE      & 0.4--0.9$\,\mu\mathrm{m}$ & 2019-09-06 03:56:25 & 58732.1642 &   & 2649  \\
\end{tabular}
\caption{Record of MACSJ0138 observations used in this work.  
The two observations from which three images of the SN were detected are marked with a '+' in column six.
\label{tab:observations}
}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{ccc}
Obs. Date (MJD) & Filter & Flux density ($\mu$Jy) \\
\midrule
57588.03 & F105W (Y) & 0.09  $\pm$ 0.02 \\
57588.03 & F105W (Y) & 2.35  $\pm$ 0.02 \\
57588.03 & F105W (Y) & 0.18  $\pm$ 0.02 \\
57587.97 & F160W (H) & 0.61  $\pm$ 0.04 \\
57587.97 & F160W (H) & 3.57  $\pm$ 0.05 \\
57587.97 & F160W (H) & 1.13  $\pm$ 0.04 \\
\end{tabular}
\caption{Photometry of the SN in MRG0138.
\label{tab:photometry}}
\end{table}

@@

\begin{table}[]
    \centering
    \begin{tabular}{c|c|c|c}
     ID &   R.A. & Dec. & $z$ \\
     \midrule
1.1 & 24.50990183 & -21.92601304 & 1.95 \\
1.2 & 24.51320906 & -21.92990322 & 1.95 \\
1.3 & 24.51641380 & -21.93031720 & 1.95 \\
1.4 & 24.51761179 & -21.92334337 & 1.95 \\
2.1 & 24.51007534 & -21.92734181 & 1.95 \\
2.2 & 24.51231984 & -21.92978758 & 1.95 \\
2.3 & 24.51512533 & -21.93066599 & 1.95 \\
3.1 & 24.5169659 & -21.9234814 & 0.7663 \\
3.2 & 24.5161061 & -21.9231225 & 0.7663 \\
3.3 & 24.5184361 & -21.9264250 & 0.7663 \\
3.4 & 24.5146833 & -21.9261020 & 0.7663 \\
    \end{tabular}
    \caption{Multiple images used as constraints in our parametric model. From left to right: image ID, right ascension, declination, spectroscopic redshift.  Coordinates are in the J2000 reference frame.}
    \label{tab:mulimages}
\end{table}

@@

\begin{table}[]
    \centering
    \begin{tabular}{c|c|c|c|c|}
    Image     & R.A. & Dec. & $\mu$ & $\Delta t$ \\
    & & & & [days] \\
\hline 
SN1 & 01:38:02.419     & -21:55:38.47         & 3.9$\pm$0.5   &   0.0 \\
SN2 & 01:38:02.957     & -21:55:47.26         & 7$\pm$3     & 101$\pm62$ \\
SN3 & 01:38:03.631     & -21:55:50.38         & 5$\pm$1     &  19$\pm34$\\
SN4 & 01:38:04.15$\pm$0.36 & -21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7760.0$\pm$540\\
%SN.1 & & & 3.907$\pm$0.534 &   0.0 \\
%SN.2 & & & 7.381$\pm$3.044 & 101.4$\pm62$ \\
%SN.3 & & & 5.020$\pm$1.217 &  19.3$\pm34$\\
%SN.4 & -5.22$\pm$0.36 &6.99$\pm$0.43 & 0.377$\pm$0.187 & 7761.0$\pm$541\\
%SN.5 & & & & \\
\hline 
\end{tabular}
    \caption{Magnifications and time delays predicted by the lens model at the location of each supernova image. Coordinates are given in the J2000 reference frame, as measured for images 1-3 and as predicted for image 4. Uncertainties in the predicted position of image 4 are in arcseconds.}
    \label{tab:snpred}
\end{table}

@@

    \multicolumn{1}{c}{Model} &\multicolumn{1}{c}{$\mu_1$} & \multicolumn{1}{c}{$\mu_2$} &\multicolumn{1}{c}{$\mu_3$} &\multicolumn{1}{c}{$t_2-t_1$} & \multicolumn{1}{c}{$t_3-t_1$}& \multicolumn{1}{c}{$t_4-t_1$} & \multicolumn{1}{c}{Bayesian Evidence}\\
\midrule
\textit{A} & 6.324 & 9.526 & 6.879 & 180.3 & 82.7&7402.8&$-10.98\pm0.28$ \\
\textit{B} & 6.281 & 9.923 & 7.472 & 184.4 & 85.3&7034.9&$-10.21\pm0.27$ \\
\textit{C} &8.942  & 18.48 & 13.257 & 103.6 & 50.2&5876.8&$-6.91\pm0.22$ \\
\textit{D} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-7.78\pm0.24$ \\
\textit{E} & 3.907 & 7.381 & 5.020 & 101.4 & 19.3&7761.0&$-6.95\pm0.2$ \\
\end{tabular}
\caption{\label{tab:model_evidence}Predicted lensing observables and Bayesian evidence for the five lens model variants investigated in this work. The Bayesian evidences in the final column are calculated by comparison to the observed photometry, using a coarse (100 live points) nested sampling fit, which helps identify models C and E as preferred over A,B, and D. We then implement a finer nested sampling fit (1,000 live points), and find that in fact model E is preferred at $>3\sigma$ ($Z_C=7.25\pm0.07, \ Z_E=7.00\pm0.06$).}
\end{table}

>>>>

One promising method uses %time delays of 
gravitational lens systems in which a background
source appears as multiple images that arrive to the observer with relative delays \cite{einstein_lens_1936}.
%, which %for a given lens potential 
When such a strongly-lensed source is variable, one can measure the time delay between any pair of lensed images and derive a ratio of angular diameter distances to the foreground lens and background source. 
This distance ratio is sensitive to cosmological parameters, such as 
%the expansion rate of the universe, 
$H_0$  and the dark energy equation of state, $w$ \cite{refsdal_possibility_1964,coe_cosmological_2009,linder_lensing_2011}.
In recent years this method has been very successfully applied to lensed
quasars \cite{suyu_cosmology_2014,bonvin_cosmograil_2019}, with six high-precision measurements to date \cite{wong_h0licow_2019}. As this sample of time delay lenses grows to several dozen, it is expected to deliver a measurement of $H_0$ with 1\% precision \cite{suyu_cosmological_2018}.

Gravitationally lensed SN with multiple images present an attractive new addition to this field. Most notably, SN exhibit relatively simple photometric behavior, with well-understood light curve shapes and colors---a contrast to the stochastic variation of quasars.  However, the exploration of lensed SN time delay cosmography has been hindered by their rarity.  To date, there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}. The first, {\it SN Refsdal}, was a peculiar Type II SN whose image with the longest delay was missed \cite{kelly_sn_2016}. The second, {\it SN 2016geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2019}. Here we present the discovery 
of a third lensed SN resolved into multiple images: \SNABC.

@@

%BibTeX users: After compilation, comment out the following two lines and paste in
% the generated .bbl file. 
\clearpage
\begin{figure*}
    \centering
    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout_sn4.pdf}
    \caption{Overview of the MACSJ0138 cluster field and the locations of the \SNABC images  (SN1--3) and its multiply-imaged host galaxy (H1--4). The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.  Panels \emph{b}--\emph{i} show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.  The three-color images are generated from the WFC3/IR filters as indicated; panels \emph{bcde} show the imaging from 2016 July where the SN was visible and \emph{fghi} show the later imaging from 2019 July where the the SN has faded away.  Panels \emph{ei} indicate the location of the fourth image predicted to appear in $\approx$2037. All panels use the late-epoch F125W imaging for the green channel; nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, helps to constrain the relative age of each SN image and the transient classification as a likely Type Ia supernova explosion.}

    \label{fig:layout}
\end{figure*}
\clearpage
\begin{figure}[h]
    \centering
    \includegraphics[draft=False, width=\textwidth]{Paper/Figures/classification_contours_timeline.pdf}
    \caption{Classification information for SN Requiem based on its position in color-magnitude space. (left) Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green).  These population contours are drawn to enclose 68\% (interior solid lines) and 95\% (exterior shaded regions) of each SN population.  Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time. Open markers show the observed photometry of the SN. Dotted vertical lines mark the magnification correction based on the lens modeling, terminating in closed markers with error bars that show the magnitude uncertainty, which is dominated by the lens modeling uncertainty.  (right) The evolution of a typical Type Ia SN at $z=1.95$ in observed color-mag space is shown by a colored line, with the color indicating SN age in observer-frame days relative to peak brightness.  White diamonds correspond to the times labeled on the colorbar at right. Grey shading shows the typical range of luminosities observed for the Type Ia SN population in the nearby universe \cite{wang_determination_2006}. An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6}{https://plot.ly/~jpierel/6}
    \label{fig:class}
    }
\end{figure}

@@

\midrule
\textit{1}  & $112^{+20}_{-38}$ & -- & $3.9\pm0.5$ & --\\
\textit{2} & $-27^{+26}_{-6}$ & $139^{+63}_{-23}$ & $7\pm3$ & $101\pm62$ \\
\textit{3} & $88^{+15}_{-15}$ & $16^{+19}_{-19}$ & $5\pm1$ & $19\pm34$ \\
\textit{4} & -- & -- & $0.4\pm0.2$ & $7760\pm540$\\

@@

Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute, and on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 0103.A-0777(A).  Support for this work was provided by NASA through grant number HST-GO-15663 from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc. under NASA contract NAS 5-26555.  The Cosmic Dawn Center of Excellence funded by the Danish National Research Foundation under grant No. 140.

@@

\begin{table}[h]
\centering
\begin{tabular}{ccccccr}
    \multicolumn{1}{c}{Telescope} & \multicolumn{1}{c}{Instrument} & \multicolumn{1}{c}{$\lambda_\mathrm{obs}$} & \multicolumn{1}{c}{UT Date} & \multicolumn{1}{c}{MJD} & \multicolumn{1}{c}{SN} & \multicolumn{1}{c}{Exp. Time (s)}\\

\midrule
\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.156 &   & 212 \\ % AOR r58785536
\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.156 &   & 241 \\
\textit{HST}     & ACS/WFC   & F555W                     & 2016-06-03 21:50:43 & 57542.910 &   & 5214 \\
\textit{HST}     & WFC3/IR   & F160W                     & 2016-07-18 23:14:50 & 57587.969 & + & 1611 \\
\textit{HST}     & WFC3/IR   & F105W                     & 2016-07-19 00:43:47 & 57588.030 & + & 3611 \\ 
\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.608 &   & 468 \\ % AOR r58289152
\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.608 &   & 581 \\
\midrule
\textit{HST}     & WFC3/IR   & F110w                     & 2019-07-13 20:53:16 & 58677.870 &   & 706 \\ 
\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-14 22:16:01 & 58678.928 &   & 353 \\ 
\textit{HST}     & WFC3/IR   & F125W                     & 2019-07-19 21:27:30 & 58683.894 &   & 706 \\ 
\textit{HST}     & WFC3/UVIS & F814W                     & 2019-07-21 18:50:53 & 58685.785 &   & 912 \\ 
\textit{HST}     & WFC3/UVIS & F390W                     & 2019-07-21 19:01:06 & 58685.792 &   & 1272 \\ 
\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-21 22:42:22 & 58685.946 &   & 353 \\ 
\textit{VLT}     & MUSE      & 0.4--0.9$\,\mu\mathrm{m}$ & 2019-09-06 03:56:25 & 58732.164 &   & 2649  \\
\end{tabular}
\caption{Record of MACSJ0138 observations used in this work.  
The two observations from which three images of the SN were detected are marked with a '+' in column six.
\label{tab:observations}
}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{cccc}
Image & Obs. Date (MJD) & Filter & Flux density ($\mu$Jy) \\
\midrule
SN1 & 57588.03 & F105W ($Y$) & 0.09  $\pm$ 0.02 \\
SN2 & 57588.03 & F105W ($Y$) & 2.35  $\pm$ 0.02 \\
SN3 & 57588.03 & F105W ($Y$) & 0.18  $\pm$ 0.02 \\
SN1 & 57587.97 & F160W ($H$) & 0.61  $\pm$ 0.04 \\
SN2 & 57587.97 & F160W ($H$) & 3.57  $\pm$ 0.05 \\
SN3 & 57587.97 & F160W ($H$) & 1.13  $\pm$ 0.04 \\
\midrule
SN1 & 58677.87 & F110W ($Y$) & 0.01  $\pm$ 0.02 \\
SN1 & 58678.93 & F140W ($H$) & 0.02  $\pm$ 0.02 \\
SN1 & 58683.89 & F125W ($J$) & 0.02  $\pm$ 0.03 \\
\end{tabular}
\caption{Photometry of the SN in MRG0138.  The final three rows indicate ``empty'' aperture flux densities measured at the position of SN1 in the 2019 \textit{HST} visits.
\label{tab:photometry}}
\end{table}

@@

\begin{table}[]
    \centering
    \begin{tabular}{rccl}
     ID &   R.A. (deg) & Dec. (deg) & $z$ \\
     \midrule
H1 & 24.5099018 & $-$21.9260130 & 1.95 \\
H2 & 24.5132090 & $-$21.9299032 & 1.95 \\
H3 & 24.5164138 & $-$21.9303172 & 1.95 \\
H4 & 24.5176117 & $-$21.9233433 & 1.95 \\
SN1 & 24.5100753 & $-$21.9273418 & 1.95 \\
SN2 & 24.5123198 & $-$21.9297875 & 1.95 \\
SN3 & 24.5151253 & $-$21.9306659 & 1.95 \\
3.1 & 24.5169659 & $-$21.9234814 & 0.7663 \\
3.2 & 24.5161061 & $-$21.9231225 & 0.7663 \\
3.3 & 24.5184361 & $-$21.9264250 & 0.7663 \\
3.4 & 24.5146833 & $-$21.9261020 & 0.7663 \\
    \end{tabular}
    \caption{Multiple images used as constraints in our parametric model. From left to right: image ID, right ascension, declination, spectroscopic redshift.  Coordinates are in the J2000 reference frame.}
    \label{tab:mulimages}
\end{table}

@@

\begin{table}[]
    \centering
    \begin{tabular}{c|l|l|c|c|}
    Image     & R.A. & Dec. & $\mu$ & $\Delta t$ \\
    & & & & [days] \\
\hline 
SN1 & 01:38:02.42     & $-$21:55:38.47         & 3.9$\pm$0.5   &   --- \\
SN2 & 01:38:02.96     & $-$21:55:47.26         & 7$\pm$3     & 101$\pm62$ \\
SN3 & 01:38:03.63     & $-$21:55:50.38         & 5$\pm$1     &  19$\pm34$\\
SN4 & 01:38:04.15$\pm$0.36 & $-$21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7760$\pm$540\\
%SN.1 & & & 3.907$\pm$0.534 &   0.0 \\
%SN.2 & & & 7.381$\pm$3.044 & 101.4$\pm62$ \\
%SN.3 & & & 5.020$\pm$1.217 &  19.3$\pm34$\\
%SN.4 & -5.22$\pm$0.36 &6.99$\pm$0.43 & 0.377$\pm$0.187 & 7761.0$\pm$541\\
%SN.5 & & & & \\
\hline 
\end{tabular}
    \caption{Magnifications and time delays predicted by the lens model at the location of each supernova image. Coordinates are given in the J2000 reference frame, as measured for images 1--3 and as predicted for image 4.  Uncertainties in the predicted position of image 4 are in arcseconds.  Time delays are reported relative to SN1.}
    \label{tab:snpred}
\end{table}

@@

    \multicolumn{1}{c}{Model} &\multicolumn{1}{c}{$\mu_1$} & \multicolumn{1}{c}{$\mu_2$} &\multicolumn{1}{c}{$\mu_3$} &\multicolumn{1}{c}{$t_2-t_1$} & \multicolumn{1}{c}{$t_3-t_1$}& \multicolumn{1}{c}{$t_4-t_1$} & \multicolumn{1}{c}{Bayesian Evidence}\\
\midrule
\textit{A} & 6.324 & 9.526 & 6.879 & 180.3 & 82.7&7402.8&$-10.98\pm0.28$ \\
\textit{B} & 6.281 & 9.923 & 7.472 & 184.4 & 85.3&7034.9&$-10.21\pm0.27$ \\
\textit{C} &8.942  & 18.48 & 13.257 & 103.6 & 50.2&5876.8&$-6.91\pm0.22$ \\
\textit{D} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-7.78\pm0.24$ \\
\textit{E} & 3.907 & 7.381 & 5.020 & 101.4 & 19.3&7760&$-6.95\pm0.2$ \\
\end{tabular}
\caption{\label{tab:model_evidence}Predicted lensing observables and Bayesian evidence for the five lens model variants investigated in this work. The Bayesian evidences in the final column are calculated by comparison to the observed photometry, using a coarse (100 live points) nested sampling fit, which helps identify models C and E as preferred over A,B, and D. We then implement a finer nested sampling fit (1,000 live points), and find that in fact model E is preferred at $>3\sigma$ ($Z_C=7.25\pm0.07, \ Z_E=7.00\pm0.06$).}
\end{table}
